Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2024-06-11 paper/1_Initial/manuscript.qmd
let's not use gt

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Factor structure and correlates"
author:
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles:
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
---

@@

A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g. *"I can always accurately perceive when I need to urinate"*).
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., ***"I trust my body sensations"***, ***"I can notice an unpleasant body sensation without worrying about it"***).

@@

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 9 studies was included.
Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
**See Table 1 (add crossref link)** for a summary of the samples demographics.

**Table 1**

Samples demographics.
![Figure 1. Different ways in which interoception can be measured.](figures/table1.png){width="580"}

>>>>

---
title: "Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates"
shorttitle: "IAS Factor structure and correlates"
author:
  - name: Magdalena Pfaff
    corresponding: true
    orcid: 0009-0006-2386-7936
    # roles: 
      # - Project administration
      # - Data curation
      # - Formal Analysis
      # - Investigation
      # - Visualization
      # - Writing – original draft
      # - Writing – review & editing
    affiliations:
      - id: id1
        name: "University of Sussex"
        department: School of Psychology
        # address: 1234 Capital St.
        # city: New York
        # region: NY
        # country: USA
        # postal-code: 12084-1234
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
    #   - Writing – review & editing
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    # roles:
    affiliations:
      - ref: id1 
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    # Select from the CRediT: Contributor Roles Taxonomy https://credit.niso.org/
    # roles:
    affiliations:
      - ref: id1 
keywords: []
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-docx: default
  apaquarto-html: default
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

@@

A recently developed scale with a rapidly growing popularity is the Interoceptive Accuracy Scale [IAS; @murphy2019].
The IAS consists of 21 Likert-scale items that query how accurately one can perceive different bodily signals, with one item per physiological mechanism such as respiration (*"I can always accurately perceive when I am breathing fast"*), heart (e.g *"I can always accurately perceive when my heart is beating fast"*), skin (e.g *"I can always accurately perceive when something is going to be ticklish"*), arousal or bodily functions like coughing (e.g *"I can always accurately perceive when I am going to cough"*), urinating (e.g. *"I can always accurately perceive when I need to urinate"*).
Interestingly, the IAS' statements are about specific interoceptive behaviours, which is notable difference with other popular interoception questionnaires, such as the Multidimensional Assessment of Interoceptive Awareness scale [MAIA, @mehling2012], which items are more general and metacognitive (e.g., *"I trust my body sensations"*, *"I can notice an unpleasant body sensation without worrying about it"*).

@@

```{r}
#| warning: false
#| label: tbl-samples
#| tbl-cap: "Blabla caption fds Samples demographics"
# #| apa-note: "Some note bedlow the table"

table <- data.frame(
  Studies = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', '***Total***'),
  Samples = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', 451, 375, 814, 515, 802, 96, 619,'', 522, 1993, 802,'', 1166, 500, 21843, 485, 251, "\\textbf{31317}"),
  Age = c('', "25.8 ± 8.4 [18-69]", 35.3, 24.9, 30.7, 36.58, 28.78, 43.9,'', 23.4, 32.0, 27.3,'', 32.5, 37.4, 56.5, 30.1, 37.5, 49.5),
  SD = c('', 8.4, 16.9, 5.3, 10.5, 12.41, 27.5, 14.5,'',  6.7, 12.6, 9.3, '', 8.4, 7.4, 14.4, 10.1, 13.2, 13.2),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Link= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'In preparation **', 'In preparation **', '')
)

knitr::kable(table, format = "latex", booktabs = TRUE, longtable = TRUE, col.names = stringr::str_replace(names(table), "Female_Percentage", "Female %")) |> 
  kableExtra::kable_styling(font_size = 7)
```

Our search focused on studies citing the original IAS validation paper [@murphy2019], identifying 136 papers (as of **XX/XX/2024**).
To qualify for inclusion, papers needed to (1) provide accessible data in open-access, (2) employ the IAS as a measure, and (3) report individual IAS items scores.
A total of 9 studies was included.
Additionally, we added datasets of two unpublished (but already open-access) studies from our lab.
**See @tbl-samples** for a summary of the samples demographics.
